Control estadístico de procesos

### 2017-12-27 01_IntroduccionAR/IntroduccionAR.Rmd
Working on "Introduccion A R". Adapting CSS

---
title: "Control estadístico de procesos"
subtitle: "Introducción a R"
author: "Jordi Cuadros, Lucinio González"
date: "Diciembre de 2017"
output: ioslides_presentation
---

@@

https://www.r-project.org/about.html

>>>>

---
title: "Control estadístico de procesos"
subtitle: "Introducción a R"
author: "Jordi Cuadros, Lucinio González"
date: "Diciembre de 2017"
logo: "../images/IQSlogo.png"
css: "../css/styles.css"
output: ioslides_presentation
---

@@

https://www.r-project.org/about.html
https://www.rdocumentation.org/
https://stackoverflow.com/questions/tagged/r
